MLExplain

### 2018-07-23 paper.tex
added the reviews, started to address them
adding screenshot, minted

%\documentclass{article}
\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,shapes,arrows.meta}
\usepackage{hyperref}

\author{ K\'evin Le Bon \and Alan Schmitt }

\title{MLExplain}

@@

@@

\begin{figure*}[t]
  \centering
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpreter and libraries (OCaml)};

@@

\begin{verbatim}
let bind_option opt f = match opt with
| Some value -> f value
| None -> None
\end{verbatim}

To use this operator, one would need to write the following.
\begin{verbatim}
bind_option
  (function_that_could_fail 0)
  (fun a -> continuation a)
\end{verbatim}
Such code can become difficult to read, especially when one is chaining several
functions.

The use of \texttt{ppx} lets us write much simpler code, which is transformed to
the previous version during parsing.
\begin{verbatim}
let%some a = function_that_could_fail 0 in
continuation a
\end{verbatim}

@@

@@

\begin{figure}[hb]
  \begin{tabular}{| c | c | c | c |}
    \hline
    & Comments & Code & Bind calls \\
    \hline
    Interpreter & 164 & 394 & 62 \\
    Primitives & 31 & 35 & 0 \\
    Execution context & 22 & 13 & 0 \\
    Frontend & 41 & 542 & 0 \\
    Syntax definition & 17 & 65 & 0 \\
    Auxiliary files & 72 & 232 & 2 \\
    \hline
    Total (no .mli) & 392 & 1621 & 70 \\
    Total (with .mli) & 401 & 1636 & 70 \\
    \hline
  \end{tabular}

@@

>>>>

%\documentclass{article}
\documentclass[twocolumn,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=1cm, bottom=2cm, left=1.5cm, right=1.5cm]{geometry} 
\usepackage{minted}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,shapes,arrows.meta}
\usepackage{hyperref}

\author{ K\'evin Le Bon (Inria) \and Alan Schmitt (Inria) }
\title{MLExplain}
\date{}

@@

Note that JSExplain, and by extension MLExplain, runs a program to its
completion to generate the trace, and it is that trace that is explored using
the web interface. It thus does not currently offer the ability to alter the
state of the program as it is being explored.

@@

\begin{figure*}
  \centering
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpreter and libraries (OCaml)};

@@

\begin{minted}{ocaml}
let bind_option opt f = match opt with
| Some value -> f value
| None -> None
\end{minted}

To use this operator, one would need to write the following.
\begin{minted}{ocaml}
bind_option
  (function_that_could_fail 0)
  (fun a -> continuation a)
\end{minted}
Such code can become difficult to read, especially when one is chaining several
functions.

The use of \texttt{ppx} lets us write much simpler code, which is transformed to
the previous version during parsing.
\begin{minted}{ocaml}
let%some a = function_that_could_fail 0 in
continuation a
\end{minted}

@@

\begin{figure*}
  \centering
  \includegraphics[width=14cm]{mlexplain.png}
  \caption{MLExplain}
  \label{fig:mlexplain}
\end{figure*}

@@

\begin{figure}
  \begin{tabular}{| c | c | c | c |}
    \hline
    & Comments & Code & Bind calls \\
    \hline
    Interpreter & 164 & 394 & 62 \\
    Primitives & 31 & 35 & 0 \\
    Execution context & 22 & 13 & 0 \\
    Frontend & 41 & 542 & 0 \\
    Syntax definition & 17 & 65 & 0 \\
    Auxiliary files & 72 & 232 & 2 \\
    \hline
    Total (no .mli) & 392 & 1621 & 70 \\
    Total (with .mli) & 401 & 1636 & 70 \\
    \hline
  \end{tabular}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-engine: latex_sh
%%% End:
